---
title: "STAT 433 Week 3"
author: "Zeyang Yu"
date: "2022-09-26"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(nycflights13)
library(ggplot2)
library(tidyverse)
```


1.How many flights have a missing dep_time? What other variables are missing? What might these rows represent?

```{r}
summary(flights)
```

There are 8255 flights have a missing dep_time. Also, there are 8255 flights have a missing dep_delay, 8713 flights have a missing arr_time, 9430 flights have a missing arr_delay and 9430 flights have a missing air_time. Probably those flights were canceled or the data was lost. 


2.Currently dep_time and sched_dep_time are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.

```{r}
mutate(flights,
       dep_time = (dep_time %/% 100) * 60 + (dep_time %% 100),
       sched_dep_time = (sched_dep_time %/% 100) * 60 + (sched_dep_time %% 100))
```


3.Look at the number of canceled flights per day. Is there a pattern? Is the proportion of canceled flights related to the average delay? Use multiple dyplr operations, all on one line, concluding with ggplot(aes(x= ,y=)) + geom_point()


```{r}
flights %>%
  mutate(cancelled = (is.na(arr_delay) | is.na(dep_delay))) %>%
  group_by(year, month, day) %>%
  summarise(
    cancelled_prop = mean(cancelled),
    avg_dep_delay = mean(dep_delay, na.rm = TRUE),
    avg_arr_delay = mean(arr_delay, na.rm = TRUE)
  ) %>%
  ggplot(aes(x = avg_dep_delay, y = cancelled_prop)) +
  geom_point()
```
According to the plot, with the increasing of average departure delay and
and average arrival delay flights, the proportion of cancelled flights also increases. 
